\chapter{Background and Theory}

Vector graphics have been popular in the computer industry for many years,
seeing frequent use in analogue oscilloscopes, video arcade games \cite{astroids},
and as display devices for computers \cite{ibm2250}. 
This chapter introduces the concept of vector graphics, and compares it to it's counterpart, the raster graphic.

\section{Computer Graphics}
Computer graphics, introduced around 1960\cite[sec. 1.1.1]{graphics-visualization-algorithms}, is the huge branch in today's computing world that deals with imagery and animations produced by a computer.
At it's core, this project deals with the type of computer graphics defined as vector graphics, which is detailed further in this section. 
Since the project also involves what is known as raster graphics, the team has decided to detail this in the section as well.

\input{content/introduction/background/2D-raster-graphics}
\input{content/introduction/background/2D-vector-graphics}
\input{content/introduction/background/3D-graphics}

\section{Visual Displays}
In the early days of computer display, vector displays were mainly used.
The use of frame buffers started when transistor-based RAM was introduced.
As a result, raster graphics and displays were created. \cite[sec. 1.1]{graphics-visualization-algorithms}.

Today, there exists a vast variety of display technologies - a few examples are CRT, LCD, LED and OLED.
This section discusses vector displays and raster displays, and follows with a comparison between the two. It ends with an introduction to an oscilloscope, which was used in the project to output the vector graphics.

\input{content/introduction/background/raster-display}
\input{content/introduction/background/vector-display}
\input{content/introduction/background/display-comparison}
\input{content/introduction/background/oscilloscope}

\section{Primitives}

In vector graphics an image is created by assembling a set of figures into a more complex image.
These base figures are for example lines, circles, ellipses or curves.

\subsection{Bézier curves}

A very popular type of curve in vector graphics is Bézier curves.
Bézier curves can represent everything from a straight line to very complex paths with a lot of turns and changes in direction.
A Bézier curve is defined by a series of control point ranging from \(P_0\) to \(P_n\). 
n is called the order of the curve and as such you end up with linear (n = 1), quadratic (n = 2), and cubic (n = 3) Bézier curves.
Below the formulas for some frequently used Bézier curves are shown. B(t) is the point on the curve at t.
As t can be incremented as little or as much as wanted points on the curve can be calculated as granularly as desired.

\begin{cequation}[H]
	\begin{equation*}
		\mathbf{B}(t)=\mathbf{P}_0 + t(\mathbf{P}_1-\mathbf{P}_0)=(1-t)\mathbf{P}_0 + t\mathbf{P}_1 \mbox{ , } 0 \le t \le 1
	\end{equation*}
	\caption{Linear Bézier curve}
\end{cequation}

\begin{cequation}[H]
	\begin{equation*}
		\mathbf{B}(t) = (1 - t)^{2}\mathbf{P}_0 + 2(1 - t)t\mathbf{P}_1 + t^{2}\mathbf{P}_2 \mbox{ , } 0 \le t \le 1
	\end{equation*}
	\caption{Quadratic Bézier curve}
\end{cequation}

\begin{cequation}[H]
	\begin{equation*}
		\mathbf{B}(t)=(1-t)^3\mathbf{P}_0+3(1-t)^2t\mathbf{P}_1+3(1-t)t^2\mathbf{P}_2+t^3\mathbf{P}_3 \mbox{ , } 0 \le t \le 1
	\end{equation*}
	\caption{Cubic Bézier curve}
\end{cequation}
