\subsection{Vector Display}
A vector display or monitor, is a device that draws graphics from point to point.
// TODO: As opposed to?
A vector monitor utilizes CRT (Cathode Ray Tube) technology, which contain one or more electron guns and a phosphorescent screen to view images.
The electron beam is deflected horizontally and vertically using electrostatic deflection. \cite{vector-monitor}

Unlike the CRT raster displays (old television sets or computer monitors), a vector monitor does not scan repeatedly in a fixed pattern.
Instead it draws a point based on two voltages, one for horizontal placement and one for vertical. Dark areas are never visited by the electron beam.

Refresh rate depends on which type of phosphor is used. Some phosphor types fade out very quickly and needs refreshing 30-40 times per second. 
Special types can last for minutes.

Vector monitors with limited color support exist. 
By using a shadow mask between the electron guns and the screen, and having one electron gun for red, green and blue, RGB colors can be displayed on screen.

There are notable advantages with vector monitors:
\begin{itemize}
\item Since they are able to draw directly from one point to another, they do not suffer from artefacts like aliasing and pixelation.
\item The entire screen is not updated every time, only the areas that the beam visits.

There is major disadvantages with vector screens however:
\begin{itemize}
\item Graphics on vector screens are very limited compared to raster screens, because of crude line drawing and limited, to single color support.
\item The refresh rate is also limited. When a bigger area of the screen is drawn, the screen starts to flicker more and more.
\item Irregular beam motion is slower than raster screens' predictable scanning.
\end{itemize} 

Vector displays are pretty much obsolete today, because raster screens are inexpensive and support graphics with a higher level of detail.
Algorithms for graphic generation on raster screens were also much simpler than corresponding algorithms for vector screens.

\subsubsection{Oscilloscope}
As vector monitors are no longer a easily available, the group needed to find an alternative method of displaying vector graphics, preferrably without rasterization involved.
It is possible to modify a CRT monitor, so that one can manually control the deflectors, but this is quite cumbersome.
The other method is using an oscilloscope, which gives an easy interface to these deflectors.
This section will explain how to use the oscilloscope as a vector monitor.


To be able to draw to a oscilloscope, the oscilloscope must support at least two input channels, and the ability to draw in X-Y mode.
In X-Y mode, two of the input channels (usually Ch1 and Ch2) governs the electron ray deflectors.
If the channels are provided a constant voltage, a dot will be displayed on the screen, in contrast to normal mode, where  a line would be drawn.

The voltage on channel 1 will normally decide the beam's horizontal position, and channel two, its vertical position.
To draw a line on the oscilloscope, one would need to repeatedly change the voltage of one or both channels back and forth.
Changing the voltage on only one channel will produce a horizontal or vertical line.
