\chapter{Discussion}

The group faced some issues during the design process.
This chapter discusses the significant obstacles encountered, and how the group managed to fix or work around them.
Additionaly, possible improvements that were thought about are addressed in the section's end.

\input{content/results/pcb-discussion}

\section{Component Ordering}
The group feels they could've been more thorough with datasheet inspection before finalising component orders.
While waiting for the first delivery, it was discovered that the ordered \gls{led}s were reverse mounted, and not compatible with the \gls{pcb}.
Hence, a new set of \gls{led}s with the correct footprint were ordered.
While this was a cheap component, it could very well have been an important component, resulting in unnecessary delays and waste of money.

Several \gls{dac}s were destroyed, caused by short-circuits during testing.
This resulted in a shortage of \gls{dac}s, which were essential for the design.
For future reference a surplus of fragile components should be ordered.

\input{content/results/oscillator}

\section{Drawing Artefacts}
\label{discussion:artefacts}
The drawing artefacts explained in Section \ref{results:artefacts} are possible to remove.
If a third input value for intensity were to be added, one could turn the electron beam off when moving the beam between primitives.

The other artefact mentioned, the dotted lines, could be removed by adding analogue circuitry between the \gls{dac} output and the BNC connectors.
It is possible to slew the electron beam from one point to the next, using analogue integration, to archive a smooth transition between points.
An example of such circuitry has been implemented in the 80's in a similar project \cite{vector-graphic-crt}.

If \vthreek were to support an intensity value in addition to x and y, the architecture and \gls{pcb} would require changes.

\section{Improvements}
Further improvements - which ultimately were not implemented due to time constraints or complexity - were discussed by the group and are detailed here.

Before any actual coding and soldering, the group spent some time planning the architecture. It was argued that implementing floating point would better conform to the industry standards of vector calculation, and that it would offer more precise calculations.

The auto router caused some wires to make long detours.
More manual routing of signals could've generally shortened these distances.
Wires in the same parallel buses should ideally have equal lengths, to ensure all signals in are synchronized.

The final implementation of the processor is a multi-cycle RISC/MIPS inspired processor.
In this design, one instruction is executed each for second or third clock cycle.
To increase the number of instructions per cycle, the processor could have been pipelined.
Given the time constraint, the group never found the time to implement a pipelined processor.

The processor could also have been made into a multi-core processor, which would further improve the performance. Ultimately, time constraints caused this project to come to a halt.

Interactivity between the user and the graphics could have been implemented, using the included buttons and joystick. A game was discussed as a possible demo, but was deemed to complex and time demanding, given that other parts of the system were more critical to implement.

A toolchain to make it easier for programmers to program on the computer was not prioritised high enough to be done anything with.

The \gls{isa} could have been extended, i.e. with convenient operations that would shorten the program length and solve unintuitive syntax.
