\section{Physical PCB and Components testing}

// TODO: Restructure this, some of it belongs in results, some in discussion.

When we had received the PCB and the components, we had to make sure that every component worked properly independent of the PCB, then testing if they worked on the PCB. Many major components were impossible to test without soldering on the PCB though. Examples were the FPGA and MCU, because of their tiny ball grid pins.

\subsection{Soldering}
There were different ways of soldering components on the PCB. It depended on components being through hole, surface mounted, pin size, etc.
\subsubsection{Ball Grid Arrays (BGA)}
Both the FPGA and MCU were ball grid arrays.
Therefore, they were soldered on the PCB, by smearing paste over the corresponding area, putting them carefully on, and putting the PCB in a heater. The heater made the components stick properly to the paste. This was the only way, since soldering pins directly under the component by hand, isn't practically possible.

\subsubsection{Surface Mounted Components}
Most surface mounted components where the pins weren't too small and crowded, were soldered by hand. Paste were used before hand, just like with BGAs, but after that the pins could be soldered by hand, since the pins were within physical reach. 
\newline
If pins were too small and tight, the same technique was used as for the BGAs.

\subsubsection{Through Hole Components}
Through Hole components were the easiest to solder, since the pin size and the space between them was relatively large. Additionally they were on the bottom side of the board. No paste was needed, each individual pin could be soldered with tin wires.

\subsection{Testing of Physical PCB}
We had to find and fix all errors and faults with our PCB design and components, that were a hazard to our desired resulting system.  
We had some direct initial tests of the PCB itself, but afterwards it was indirectly tested, when testing the FPGA, MCU, DACs etc. It was in these indirect tests, most errors were discovered.

Testing was done by using a multimeter and oscilloscopes. Using a multimeter was the best way to verify if a signal was having the expected voltage level, and if there was any current flow at all.

Oscilloscopes were handy for testing our oscillators, to check the frequency and accuracy. Note that the oscilloscope which was used as our vector display was not part of this testing. These were modern oscilloscopes, which had raster screens and operating systems installed.

\subsection{PCB Placement and Footprints}


It would have been beneficial if we had placed the 3.3V voltage regulator closer to the JTAG debugging port, since the Xilinx JTAG platform cable required a 3.3V power supply.
\newline
\newline
The micro USB footprint originally contained mounting holes, but were wrongly removed before manufacturing. Luckily, these did not act as connectors, and we could therefore solder the USB receptacle onto the PCB like a surface mount component.

\subsection{Component Order Issues}
The initial LEDs we ordered were reverse mounted, meaning that they required a hole in the board and had to be soldered on to the bottom layer. Because of this, we had to buy some new ones.
\newline
\newline

\subsection{Component sizes}
In hindsight, it would have been better to order bigger components. Since this is a prototype board where we mostly solder by hand, an increase in size would only be beneficial for us. If the project should go into large scale production, we could have tried to shrink the size.